Leveraging Diversity to Find Bugs\\ in JavaScript Engines

### 2018-08-25 paper/paper.tex
pass on abstract, macros, and tables
checking macros

\emph{Results.}~\Fix{REVISE}We considered engines from four major players--Apple,
Google, Microsoft, and Mozilla. Our results indicate that both
techniques revealed several bugs, most of which confirmed by
developers. Test transplantation revealed \noBugsTransplantation{}
bugs (\noBugsTransplantationConfirmed{} confirmed) and differential
testing revealed \noBugsDifferentialTesting{} bugs
(\noBugsDifferentialTestingConfirmed{}). Furthermore, results indicate
that most of these bugs affected only two engines--Apple's \jsc{}
(\percJSC{}) and Microsoft's \chakra{} (\percChakra{}); we found only
one bug in Google \veight{} and none in Mozilla's \smonkey{}. Although
our experience indicates that more research needs be done to automate
parts of the inspection process, our results show that exploring
diversity is a valuable help to find bugs in JavaScript engines.

%% LIST OF CONTRIBUTIONS
\emph{Contributions.}~This paper contributes the following:
\begin{itemize}
  \item We ran a comprehensive study to analyze the effectiveness of
    simple diversity-aware techniques to find bugs in highly-popular
    \js\ engines.

  \item We reported more than \Fix{50} bugs on these engines over a
    period of 5 months.

@@

\vspace{1ex}
\noindent\textbf{Summary of Bugs.}~Figure~\ref{fig:summary} shows the
number of bug reports found per engine (\ref{fig:stacked-engine}) and
technique (\ref{fig:stacked-technique}). Each stacked bar breaks down
the bugs per status (\eg{}, ``1-New''). The prefix number serves to
indicate the ordering that status labels are assigned. Note that
several of these reports have the label ``3-Fixed'', indicating that
bug fixes have been incorporated into the code already.\Comment{
  Depending on the issue date, the fix may be in the latest release of
  the corresponding engines.} Overall, discarding bug report with the
``1-New'' status, we reported a total of \noBugsTotalConfirmed{}
bugs. We found that the majority of bug reports targeted the engines
from Microsoft and Apple. Considering the techniques, the number of
bug reports were similar, if we consider only those confirmed or
fixed. Most of these bugs are of moderate severity. All in all, these
simple techniques seem promising to improve reliability of engines
that continuously evolve with their specifications.

@@

\begin{figure}[h!]
  \centering
  \subfloat[\label{fig:stacked-engine}Bug reports per engine.]{
    \includegraphics[trim=0 190 0 180,clip,width=0.45\textwidth,scale=0.4]{R/stackedbar/stacked-engine}
    \vspace{-5ex}
  }\\
  \subfloat[\label{fig:stacked-technique}Bugs reports per technique.]{
    \includegraphics[trim=0 180 0 180,clip,width=0.45\textwidth,scale=0.4]{R/stackedbar/stacked-technique}
    \vspace{-5ex}        
  }
  \caption{\label{fig:summary}Summary of bug reports.}
\end{figure}

@@

\begin{wraptable}[10]{r}{0.25\textwidth}
%  \vspace{-3ex}
  \centering
  \caption{\label{tab:test262}Percentage of passing tests on
    the Test262 conformance suite.}
  \small
  \begin{tabular}{crr}
    \toprule
    engine & \% passing \\
    \midrule
    \jsc{} & 92\%\\
    \veight{} & 95\% \\
    \chakra{} & 75\% \\    
    \smonkey{} & 93\% \\
    \bottomrule
  \end{tabular}
  \normalsize
\end{wraptable}
We used the official conformance test suite
Test262~\cite{ecma262-conformance-suite} to evaluate conformance of
engines to the \js\ current standard. As it is acceptable to release
engines fulfilling the specification only partially~\cite{kangax}, it
is expected that engines do not fully pass this test. However, we
expect that results provide indication of engine's maturity. In the
limit, it is not desirable to flood bug reports on engines at early
stages of development. We ran the suite once a day for seven
consecutive days from the period of 16 to 22 of August,
2018. Table~\ref{tab:test262} shows the average number of passing
tests over this period. The variance of results was negligible; for
that reasons, we omited standard deviations. We noticed that all four
engines we analyzed but \chakra{} use some variant of the Test262
suite as part of their regression process, but we used the same
version in this experiment; the one available from the Test262 web
site~\cite{ecma262-conformance-suite}. Results show that there are
still many unsupported cases as can be observed from the percentages
in the table, but the number of passing tests is high, with
\veight\ and \smonkey\ performing better compared to others and
\chakra\ performing well worse than others. It is important to
highlight that failures in this conformance test suite indicates
missing features as opposed to bugs. However, note that \chakra\ is
both the engine that has the lowest passing ratio in the conformance
test suite and the one we were able to find more bugs. Although it is
possible to find correlation between the percentage of passing tests
in the conformance suite (as per Table~\ref{tab:test262}) and reliability as
measured by the number of bugs found (as per
Figure~\ref{fig:summary}), we do not not imply causality.

@@

\begin{table}[h!]
  \setlength{\tabcolsep}{4pt}    
  \centering
  \caption{\label{fig:falsepositives}\label{fig:truepositives}\label{fig:piecharts-transplantation}Distribution of false and true positives.}
  \begin{tabular}{ccr}
    \toprule
    & source &  \#\\
    \midrule
    \multirow{5}{*}{False Positives} & Undefined Behavior & 313 \\
    & Timeout/OME & 15 \\
    & Not Implemented & 22 \\
    & Non-Standard Element & 177 \\
    & Unknown & 135 \\
    \midrule
    \multirow{2}{*}{True Positives} & Duplicate & 10 \\
    & Bug & 24 \\
    \bottomrule
  \end{tabular}
\end{table}

@@

Table~\ref{fig:piecharts-transplantation} shows the distribution of
false and true positives. Considering false positives, ``Undefined
Behavior'' and ``Non-Standard Element'' were the most predominant
sources. Considering true positives, we found a reasonable number of
duplicate reports, but not enough high to justify attempting to
automate the detection of duplicates.
Table~\ref{tab:test-transplantation-bugs} lists all bugs we found with
test transplantation. The first column shows the identifier we
assigned to the bug\Comment{, column ``Date'' shows the date the bug
  was reported in the format ``m/dd'',}, column ``Engine'' shows the
affected engine, column ``Status'' shows the status of the bug report
at the time of the writing. The status string appears in bold face for
status ``Confirmed'' or higher, \ie{}, ``Assigned'' and ``Fixed''.
Column ``Url'' shows the URL (de-anonymized upon request) for the bug
report entry in the corresponding bug-tracking system, column
``Severity'' shows the severity level for confirmed bugs, and,
finally, column ``Suite'' shows the name of the engine that originated
the test. Note that bug reports \#4 and \#23 afected multiple
engines.

>>>>

\emph{Results.}~We considered engines from four major players--Apple,
Google, Microsoft, and Mozilla. Our results indicate that both
techniques revealed several bugs, most of which confirmed by
developers. Test transplantation revealed \noBugsTransplantation{}
bugs (of which, \noBugsTransplantationConfirmed{} were confirmed and
\noBugsTransplantationFixed{} were fixed) whereas differential testing
revealed \noBugsDifferentialTesting{} bugs (of which,
\noBugsDifferentialTestingConfirmed{} were confirmed and
\noBugsDifferentialTestingFixed{} were fixed). Furthermore, results
indicate that most of these bugs affected two engines--Apple's \jsc{}
and Microsoft's \chakra{}.  We reported \noBugsBugsReportedGoogle{}
bugs in Google \veight{} (\noBugsBugsConfirmedGoogle{} confirmed) and
none in Mozilla's \smonkey{}. Our results indicate that both
techniques were successful at finding bugs, but, overall, test
transplantation demanded less effort compared to differential testing
per bug found. Although our experience indicates that more research
needs be done to automate parts of the inspection process, our results
show that exploring diversity is a valuable help to find bugs in
JavaScript engines.

%% LIST OF CONTRIBUTIONS
\emph{Contributions.}~This paper contributes the following:
\begin{itemize}
  \item We ran a comprehensive study to analyze the effectiveness of
    simple diversity-aware techniques to find functional bugs in
     popular \js\ engines;

  \item We reported a total of \totalBugsReported{} bugs on these
    engines. Of which, \totalBugsConfirmed{} confirmed and
    \totalBugsFixed{} fixed;

@@

\vspace{1ex}
\noindent\textbf{Summary of Bugs.}~Figure~\ref{fig:summary} shows the
number of bug reports found per engine (\ref{fig:stacked-engine}) and
technique (\ref{fig:stacked-technique}). Each stacked bar breaks down
the bugs per status (\eg{}, ``1-New''). The prefix number serves to
indicate the ordering that status labels are assigned. Note that
several of these reports have the label ``3-Fixed'', indicating that
bug fixes have been incorporated into the code already.\Comment{
  Depending on the issue date, the fix may be in the latest release of
  the corresponding engines.} Overall, discarding bug reports with the
``1-New'' status, we reported a total of \totalBugsConfirmed{}
bugs. We found that the vast majority of bug reports targeted the engines
from Microsoft and Apple. Considering the techniques, the number of
bug reports were similar, if we consider only those confirmed or
fixed. Most of these bugs are of moderate severity. All in all, these
simple techniques seem promising to improve reliability of engines
that continuously evolve with their specifications.

@@

\begin{figure}[h!]
%  \vspace{-2ex}  
  \centering
  \subfloat[\label{fig:stacked-engine}Bug reports per engine.]{
    \includegraphics[trim=0 190 0 180,clip,width=0.45\textwidth,scale=0.4]{R/stackedbar/stacked-engine}
    \vspace{-5ex}
  }\\
  \subfloat[\label{fig:stacked-technique}Bugs reports per technique.]{
    \includegraphics[trim=0 180 0 180,clip,width=0.45\textwidth,scale=0.4]{R/stackedbar/stacked-technique}
    \vspace{-5ex}        
  }
  \caption{\label{fig:summary}Summary of bug reports.}
%  \vspace{-3ex}
\end{figure}

@@

%\begin{wraptable}[10]{r}{0.25\textwidth}
%  \vspace{-3ex}
%\end{wraptable}
\
\begin{table}[t]
  \centering
  \caption{\label{tab:test262}Percentage of passing tests on
    the Test262 conformance suite.}
  \small
  \begin{tabular}{crr}
    \toprule
    engine & \% passing \\
    \midrule
    \jsc{} & 92\%\\
    \veight{} & 95\% \\
    \chakra{} & 75\% \\    
    \smonkey{} & 93\% \\
    \bottomrule
  \end{tabular}
  \normalsize
\end{table}

We used the official conformance test suite
Test262~\cite{ecma262-conformance-suite} to evaluate conformance of
engines to the \js\ current standard. As it is acceptable to release
engines fulfilling the specification only partially~\cite{kangax}, it
is expected that engines do not fully pass this test. However, we
expect that results provide indication of engine's maturity. In the
limit, it is not desirable to flood bug reports on engines at early
stages of development. We ran the suite once a day for seven
consecutive days from the period of 16 to 22 of August,
2018. Table~\ref{tab:test262} shows the average number of passing
tests over this period. The variance of results was negligible; for
that reasons, we omited standard deviations. We noticed that all four
engines we analyzed but \chakra{} use some variant of the Test262
suite as part of their regression process, but we used the same
version in this experiment; the one available from the Test262 web
site~\cite{ecma262-conformance-suite}. Results show that there are
still many unsupported cases as can be observed from the percentages
in the table, but the number of passing tests is high, with
\veight\ and \smonkey\ performing better compared to others and
\chakra\ performing well worse than others. It is important to
highlight that failures in this conformance test suite indicates
missing features as opposed to bugs. However, note that \chakra\ is
both the engine that has the lowest passing ratio in the conformance
test suite and the one we were able to find more bugs. Although it is
possible to find correlation between the percentage of passing tests
in the conformance suite (as per Table~\ref{tab:test262}) and reliability as
measured by the number of bugs found (as per
Figure~\ref{fig:summary}), we do not not imply causality.

@@

\begin{table}[t!]
  \setlength{\tabcolsep}{4pt}    
  \centering
  \caption{\label{fig:falsepositives}\label{fig:truepositives}\label{fig:piecharts-transplantation}Distribution of false and true positives.}
  \begin{tabular}{ccr}
    \toprule
    & source &  \#\\
    \midrule
    \multirow{5}{*}{False Positives} & Undefined Behavior & 313 \\
    & Timeout/OME & 15 \\
    & Not Implemented & 22 \\
    & Non-Standard Element & 177 \\
    & Unknown & 135 \\
    \midrule
    \multirow{2}{*}{True Positives} & Duplicate & 10 \\
    & Bug & 24 \\
    \bottomrule
  \end{tabular}
\end{table}

@@

Table~\ref{fig:piecharts-transplantation} shows the distribution of
false and true positives. Considering false positives, ``Undefined
Behavior'' and ``Non-Standard Element'' were the most predominant
sources. Considering true positives, we found a reasonable number of
duplicate reports, but not enough high to justify attempting to
automate the detection of duplicates.
Table~\ref{tab:test-transplantation-bugs} lists all bugs we found with
test transplantation. The first column shows the identifier we
assigned to the bug\Comment{, column ``Date'' shows the date the bug
  was reported in the format ``m/dd'',}, column ``Engine'' shows the
affected engine, column ``Status'' shows the status of the bug report
at the time of the writing. The status string appears in bold face for
status ``Confirmed'' or higher, \ie{}, ``Assigned'' and ``Fixed''.
Column ``Url'' shows the URL (de-anonymized upon request) for the bug
report entry in the corresponding bug-tracking system, column
``Severity'' shows the severity level for confirmed bugs, and,
finally, column ``Suite'' shows the name of the engine that originated
the test.

%Note that bug reports \#4 and \#23 afected multiple engines.
